Secure Composition \\ of Robust and Optimising Compilers

### 2024-09-19 csf2/main.tex
don't make it dry

There is work on lifting exploits for single compilers to the whole chain~\cite{paykin2019weird}.
Our framework does not consider exploits.
\MP{ a bit dry and short}
%To the best of our knowledge, there does not exist published work discussing the compositionality of the robust preservation criterion, the gold-standard of secure compilation.

>>>>

There is work on lifting exploits for single compilers to the whole chain~\cite{paykin2019weird}.
%Our framework does not consider exploits.
%\MP{ a bit dry and short}
While that work considers {\em in}secure compilation and composition thereof in terms of exploits, the composition they are interested in allows to lift an exploit for one compiler pass to the whole compilation chain. 
Our framework takes the opposite direction and provides compositionality results for secure compilers.
%
%
%To the best of our knowledge, there does not exist published work discussing the compositionality of the robust preservation criterion, the gold-standard of secure compilation.
